---
title: "Keyword Expansion"
output: html_notebook
---

This is a notebook aimed at implementing the keyword expansion algorithm outlined in King et al. 2017: https://dataverse.harvard.edu/dataset.xhtml?persistentId=doi:10.7910/DVN/FMJDCD 

```{r load libraries}
library(tidyverse)
library(twitteR)
library(tidytext)
library(naivebayes)
```


The algorithm, as given in the paper:

1. Define a reference set 'R' (the kinds of docs we're looking for) and a search set 'S' (the set of documents we'll search)
*We've been working on getting a good reference set. Our search set is the set of all tweets? The set of tweets that have black keywords? For now I'm using the full set of tweets I downloaded previously*

S, then is the full tweet set, minus tweets that we've rated as about black people:
```{r}
full_tweet_set <- read_csv('data/tweets/full_tweet_sample.csv', 
         col_types = cols(.default = 'c'))
labels <- read_csv('tweet_sorter/responses/ian.csv', 
         col_types = cols(status_id = col_character()))

examples <- labels %>% filter(example==T) %>% inner_join(full_tweet_set, by = 'status_id')
not_examples <- labels %>% filter(example==F) %>% inner_join(full_tweet_set, by = 'status_id')
black_folks <- labels %>% filter(blackmen==T|blackwomen==T|blackpeople==T) %>% inner_join(full_tweet_set, by = 'status_id')
not_black_folks <- labels %>% filter(blackmen==F&blackwomen==F&blackpeople==F) %>% inner_join(full_tweet_set, by = 'status_id')
```


2. Using a diverse set of classifiers, partition all documents in S into two groups: T and S\T. 

They have a bunch of sub steps here which basically come down to using ML to sort S into docs that the models think fit with R (T) and docs that don't (S\T)

*I'm acutally just going to use naive bayes and logistic regression here. If a text gets a 1 in either of those, it gets to be in the T set*

first we'll need to prepare our labeled set
```{r prepare data}
# make a single labled df with text, status_id, and label
labeled_texts <- full_tweet_set %>% select(text, status_id) %>% filter(status_id %in% labels$status_id) %>% mutate(class_label = ifelse(status_id %in% black_folks$status_id, 1,0))

prep_texts_only <- function(df){
df <- df %>% mutate(
  text = str_replace_all(text, '(http)?(www)?\\S*(\\.com|\\.net|\\.gov|\\.be|\\.org)\\S*', ''),
  text = str_replace_all(text,"(\\w+)\\W|/(\\w+)","\\1 \\2"),
  text = str_remove(text, 'https|t.co')) # separate words joined by non-word characters

df_toke <- df %>% 
  unnest_tokens(word,text, strip_punct = TRUE) %>% # tokenize, remove punctuation
  filter(!nchar(word) < 3) %>% # remove short words
  anti_join(stop_words, by = "word") # remove stop words
df_toke <- inner_join(df_toke, df_toke %>% count(word) %>% filter(n>2), by = 'word') %>% 
  select(-n) %>% 
  mutate(present = 1) %>% 
  distinct(status_id, word, .keep_all = TRUE) %>% 
  spread(word, present, fill = 0)
if(exists('df_toke$class_label')){
  df_toke <- df_toke %>% select(status_id, class_label, everything()) 
} else {
  df_toke <- df_toke %>% select(status_id, everything()) 
}
return(df_toke)
}
```

Cool, now we'll try some NB action

```{r}
x <- as.data.frame(select(labeled_tokenized, -status_id, -class_label))
y <- labeled_tokenized$class_label
nb_model <- naive_bayes(x,y)
```

and some logistic regression

```{r}
log_model <- glm.fit(x,y,family = binomial())
```


```{r}
library(glmnet)
cv.out <- cv.glmnet(as.matrix(x),y,alpha=1,family='binomial',type.measure = 'mse' )
plot(cv.out)
coef(cv.out)
tables(nb_model)
x = NULL
for(tab in nb_model$tables){
  x <- bind_rows(x, tibble(word = names(attributes(tab)$dimnames)[[1]], prob = tab[1,2]))
}
x %>% arrange(desc(prob))
```

```{r}
# Ok, let's label some unlabeled texts:
texts_sample <- full_tweet_set %>% select(text, status_id) %>% sample_n(4000)
sample_toke <- prep_texts_only(texts_sample) %>% mutate(class_label = 3) %>% full_join(labeled_tokenized %>% filter(class_label == 2)) %>% select(names(labeled_tokenized)) %>% mutate_all(funs(replace(., is.na(.), 0)))
joined_toke <- bind_rows(sample_toke, labeled_tokenized)
joined_toke <- joined_toke %>% mutate(predict = as.numeric(predict(nb_model, newdata = joined_toke %>% select(-status_id, -class_label))))
for(tweet in full_tweet_set %>% filter(status_id %in% joined_toke$status_id[joined_toke$predict==1]) %>% select(text)){
  print(tweet)
}
word_density <- joined_toke %>% select(-status_id, -class_label)  %>% group_by(predict) %>% summarise_all(mean) %>% gather(word, prevalence, -predict)
View(word_density %>% spread(predict, prevalence) %>% mutate(diff = `2` - `1`) %>% arrange(desc(abs(diff))))
```


3. Find keywords that best classify documents into either T or S\T

  a. make the set of all possible keywords in S (all that occur more than some k times)
  b. see how good each keyword is at classifying (using precision and recall scores)
  c. rank the keywords using some statistics bs

4. Present keywords to the user, allowing them to select the ones that seem good
5. Now the user can do better keyword searches and perhaps repeat all of the steps